Benefits and risks of diversification for individual fishers

### 2017-02-18 portfolio/text/anderson-etal-rev-pfx.tex
Editing tweaks and add data statement

\affil[f]{NOAA / National Marine Fisheries Service, Alaska Fisheries Science Center, Auke
Bay Laboratories, 17109 Pt. Lena Loop Rd., Juneau, AK 99801, USA}

@@

We fit our models with Stan 2.14.1 \cite{standevelopmentteam2016,
  standevelopmentteam2016a} and R 3.3.2 \cite{rcoreteam2016}. Stan implements
the No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm \cite{hoffman2014}
to perform Bayesian statistical inference. We assigned weakly informative
priors on all parameters: \(N(0, 2^2)\) priors on all \(\beta\), \(\gamma\),
and \(\eta\) parameters, and half-\(t(3, 0, 2)\) priors (i.e.~degrees of
freedom of 3 and scale of 2) on all \(\sigma\) and \(\tau\). We ran four chains
and 2,000 iterations and discarded the first 1,000 iterations of each chain as
warm up. We checked for chain convergence visually with trace plots, ensured
that \(\hat{R}<1.05\) (the potential scale reduction factor), and that the
effective sample size, as calculated by the rstan R package
\cite{standevelopmentteam2016}, was greater than 200 for all parameters
\cite{gelman2014}. We verified that our model returned sensible estimates by
comparing our estimates to an ad-hoc two-stage model fit with the lme4 R
package \cite{bates2015}, where we first fit a mixed-effects regression model
to the mean, and then modelled the absolute residuals from that first model in
a second mixed-effects model representing the variance component. We also
validated the model with simulated data, and were able to recover the true
values (Supporting Information). Code used in our analysis is available at
\url{https://github.com/NCEAS/pfx-commercial/portfolios/}. } \showmatmethods

>>>>

\affil[f]{Alaska Fisheries Science Center, National Marine Fisheries Service, National Oceanographic and
Atmospheric Administration, Auke
Bay Laboratories, 17109 Pt. Lena Loop Rd., Juneau, AK 99801, USA}

@@

We fit our models with Stan 2.14.1 \cite{standevelopmentteam2016,
  standevelopmentteam2016a} and R 3.3.2 \cite{rcoreteam2016}. Stan implements
the No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm \cite{hoffman2014}
to perform Bayesian statistical inference. We assigned weakly informative
priors on all parameters: \(N(0, 2^2)\) priors on all \(\beta\), \(\gamma\),
and \(\eta\) parameters, and half-\(t(3, 0, 2)\) priors (i.e.~degrees of
freedom of 3 and scale of 2) on all \(\sigma\) and \(\tau\). We ran four chains
and 2,000 iterations and discarded the first 1,000 iterations of each chain as
warm up. We checked for chain convergence visually with trace plots, ensured
that \(\hat{R}<1.05\) (the potential scale reduction factor), and that the
effective sample size, as calculated by the rstan R package
\cite{standevelopmentteam2016}, was greater than 200 for all parameters
\cite{gelman2014}. We verified that our model returned sensible estimates by
comparing our estimates to an ad-hoc two-stage model fit with the lme4 R
package \cite{bates2015}, where we first fit a mixed-effects regression model
to the mean, and then modelled the absolute residuals from that first model in
a second mixed-effects model representing the variance component. We also
validated the model with simulated data, and were able to recover the true
values (Supporting Information).

The fisheries data that support the findings of this study, though
confidential, are available from the Commercial Fisheries Entry
Commission (<https://www.cfec.state.ak.us/>) and summaries used in
this paper, along with all code, are archived in a publicly available repository at
\url{https://github.com/NCEAS/pfx-commercial/portfolios/}. } \showmatmethods
